\section{Discritization}

In order to find the solution for (\ref{equ:model_system}) spatial and temporal discritizations must be made.
First the equations are discritzied by time, 
\begin{equation} \label{equ:M_time_discrit}
  \frac{M^{k+1} - M^{k}}{\Delta t} = \nabla_x (D(M^{k+1}) \nabla_x M^{k+1}) + F(C^{k+1}) M^{k+1},
\end{equation}
\begin{equation} \label{equ:C_time_discrit}
  \frac{C^{k+1} - C^{k}}{\Delta t} = \frac{h}{2} ( G(C^{k+1}) M^{k+1} + G(C^{k}) M^{k} ).
\end{equation}
Here, (\ref{equ:M_time_discrit}) follows the ideas of the Backwards Euler Method; (\ref{equ:C_time_discrit}) follows Trapezoidal Rule. 
The index variable $k$ has also been introduced in (\ref{equ:M_time_discrit} - \ref{equ:C_time_discrit}) as time step counting variable.

Now, only (\ref{equ:M_time_discrit}) requires spatial considerations since, according to the biology of our system, the substrate does not diffuse across the region.
The spatial discritization will be through the Finite Difference Method as described in \cite{saad2003iterativeMethod}.
Here a grid will be created over the region and the solution of (\ref{equ:M_time_discrit}) will be approximated at each grid point using a five-point stencil. 
This results in, 
\begin{equation} \label{equ:M_space_discrit}
  \frac{M^{k+1}_{i,j} - M^{k}_{i,j}}{\Delta t} = 
    \frac{1}{\Delta x^2} \sum_{(s,r) \in \mathbb{A}} \left( D(M^{k}_{i+\frac{s}{2}, j+\frac{r}{2}}) \cdot
    ( M^{k+1}_{i+s, j+r} - M^{k+1}_{i,j}) \right) + F(C^{k}_{i,j}) M^{k+1}_{i,j}
\end{equation}
where $\mathbb{A} = \left\{ (0, \pm1), (\pm1, 0) \right\}$.
Now there are two additional indexing variables, $i$ and $j$.
These count out the respective grid point for the spatial discritization.
On a $n \times m$ grid, the $x_1$ and $x_2$ dimensions would be represented by $i \in (0, n)$ and $j \in (0,m)$ respectivly.
One item to note is that the index on $D$ is halved because it is the arithmetic average of two adjacent values.

Now (\ref{equ:C_time_discrit}) and (\ref{equ:M_space_discrit}) can be solved as a fixed-point-iteration method.
In a single time step, the solutions for $M$ and $C$ can be solved using the previous time step solution in the follow manner:
\begin{equation} \label{equ:M_fixed_point}
  \frac{M^{p+1}_{i,j} - M^{k}_{i,j}}{\Delta t} = 
    \frac{1}{\Delta x^2} \sum_{(s,r) \in \mathbb{A}} \left( D(M^{p}_{i+\frac{s}{2}, j+\frac{r}{2}}) \cdot
    ( M^{p+1}_{i+s, j+r} - M^{p+1}_{i,j}) \right) + F(C^{p}_{i,j}) M^{p+1}_{i,j}
\end{equation}
\begin{equation} \label{equ:C_fixed_point}
  \frac{C^{p+1} - C^{k}}{\Delta t} = \frac{-1}{2} ( G(C^{p+1}) M^{p+1} + G(C^{k}) M^{k} )
\end{equation}
where $p \in (0,P)$, and for $p = 0$ we have $M^0 = M^{k}, C^0 = C^{k}$, and for $p = P$ we have $M^{P} = M^{k+1}, and C^{P} = C^{k+1}$.


