\section{Thesis Outline}

\begin{itemize}
  \item Background (1.1): Describes the placement of this problem in the existing literature.
  \item Objectives (1.2): Describes the three main objectives of this thesis.
  \item Outline (1.3): Outlines the sequencial format of the thesis.
  \item Model Description (2.1): Formulates the mathematical model that is used for the rest of the study.
  \item Nondimensionalization (2.2): The system described in the previous section is reduced to unitless parameters and variables for simplicity.
  \item Discretization (3.1): Spatial and temporal discritzations are applied to the system.
  \item Solving Technique (3.2): Using a fixed-point iteration, solutions for the system are found by use of finite difference method with the Bi-Conjugate Gradiant Method and the quadratic equation.
  \item Computational Setup (3.3): The work stations and compiler settings are recorded.
  \item Method Validation (3.4): Multiple test are run to check if the handling of the spatial discritization generated any sources or sinks in the solution. A measure to compare two the solution of two different simulations is esstablished so that a grid convergence analysis can be done.
  \item Comparison of Semi-Implicit and Fully-Implicit Methods (3.5): Using the previously established measure, the semi-implicit method and fully-implicit method are compared against varying quantities and at different tolerances.
  \item Typical Simulation (4.1): A generic simulation is run to reveal the general behaviour of the system.
  \item Travelling Wave Analysis (4.2): A travelling wave solution is suggested to exist, this is tested against different simulations to reinforce the idea.
  \item Spatial Effects (4.3): The effect of ignoring the spatial diffusion is investigated by comparing two vastly different simulations; one with evenly distributed initial condition, the other with clumped initial condition.
  \item Lessons Learned (5.1): The general findings of each section are summerized.
  \item Future Work (5.2): Possible changes and extensions are discussed.
\end{itemize}

